### Latent Semantic Scaling (LSS)

LSS is a method for measuring the semantic similarity between documents and a set of seed words. In our case, each directive or regulation is a document and the seed words convey "typical" left-right terms. The semantic similarity between documents and seed words is calculated using word embeddings provided by [GloVe](https://nlp.stanford.edu/projects/glove/). To keep computation efficient, I use the smallest pre-trained word vectors model available (6B tokens, 400K vocab, 50 dimensions).

```{r echo=FALSE, message=FALSE, warning=FALSE}
glove_polarity_scores_econ <- readRDS(here("data", "lss", "glove_polarity_scores_all_dir_reg_econ.rds"))
glove_polarity_scores_social <- readRDS(here("data", "lss", "glove_polarity_scores_all_dir_reg_social.rds"))
```

#### Seed Word: Manual Seed Words

In a first approach, I manually come up my own seed words:

```{r echo=FALSE, message=FALSE, warning=FALSE}
dict_econ <- dictionary(file = here("lss", "seed_words_econ_manual.yml"))
dict_social <- dictionary(file = here("lss", "seed_words_social_manual.yml"))

seed_econ <- as.seedwords(dict_econ$ideology, concatenator = " ")
seed_social <- as.seedwords(dict_social$ideology, concatenator = " ")
```

**Economic left seed words**
```{r echo=FALSE, message=FALSE, warning=FALSE}
left_terms <- seed_econ[seed_econ == 1]
left_terms <- names(left_terms)
left_terms
```
**Economic right seed words**
```{r echo=FALSE, message=FALSE, warning=FALSE}
right_terms <- seed_econ[seed_econ == -1]
right_terms <- names(right_terms)
right_terms
```
**Social left seed words**
```{r echo=FALSE, message=FALSE, warning=FALSE}
left_terms <- seed_social[seed_social == 1]
left_terms <- names(left_terms)
left_terms
```
**Social right seed words**
```{r echo=FALSE, message=FALSE, warning=FALSE}
right_terms <- seed_social[seed_social == -1]
right_terms <- names(right_terms)
right_terms
```

#### Seed Word: Systematic Approach

In a second approach, I apply two different models to extract seed words from text. I apply [Wordscores](https://tutorials.quanteda.io/machine-learning/wordscores/) to extract seed words from party manifestos. I also use [Wordfish](https://tutorials.quanteda.io/machine-learning/wordfish/) to extract seed words from existing legislations.

##### Wordscores

I apply the Wordscores model using reference scores from the [Manifesto Project](https://manifesto-project.wzb.eu/). Specifically, I use `rile` […].
The following tables display the top and bottom of the tables displaysing extracted Wordscore scores for terms extracted from the manifestos. Negative values are associated with left-wing terms, positive values with right-wing terms

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load all .rds files from wordscores_manifesto_datasets
rds_dir <- here("lss", "wordscores_manifesto_datasets")  # Specify the directory containing the .rds files
rds_files <- list.files(path = rds_dir, pattern = "\\.rds$", full.names = TRUE) # List all .rds files in the directory
all_wordscores_manifesto_datasets <- lapply(rds_files, readRDS) # Load all .rds files into a list

names(all_wordscores_manifesto_datasets) <- gsub("\\.rds$", "", basename(rds_files))

all_wordscores_manifesto_datasets <- lapply(all_wordscores_manifesto_datasets, function(df) {
  df %>%
    arrange(wordscores_manifesto) %>% # Replace 'token' with the column name you want to sort by
    select(-wordscores_manifesto) # Remove scores, as these are not needed for report
})
```

**RILE: Right-left position of party as given in Michael Laver/Ian Budge**  
_Most negative values (left-wing terms)_  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Set number of rows to be shown in tables
nr_of_rows <- 3

print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_1"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_2"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_3"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_1_head.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_2_head.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_3_head.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_4_head.csv)
  
_Most positive values (right-wing terms)_
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_1"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_2"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_3"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_rile_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_1_tail.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_2_tail.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_3_tail.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_rile_ngram_4_tail.csv)


**Planeco: per403 + per404 + per412**  
_Most negative values (left-wing terms)_
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_1"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_2"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_3"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_1_head.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_2_head.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_3_head.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_4_head.csv)

_Most positive values (right-wing terms)_
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_1"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_2"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_3"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_planeco_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_1_tail.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_2_tail.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_3_tail.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_planeco_ngram_4_tail.csv)

**Markeco: per401 + per414**  
_Most negative values (left-wing terms)_
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_1"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_2"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_3"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_1_head.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_2_head.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_3_head.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_4_head.csv)

_Most positive values (right-wing terms)_
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_1"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_2"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_3"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_markeco_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_1_tail.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_2_tail.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_3_tail.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_markeco_ngram_4_tail.csv)

**Welfare: per503 + per504**  
_Most negative values (left-wing terms)_
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_1"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_2"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_3"]], nr_of_rows), row.names = FALSE)
print(head(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_1_head.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_2_head.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_3_head.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_4_head.csv)

_Most positive values (right-wing terms)_
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_1"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_2"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_3"]], nr_of_rows), row.names = FALSE)
print(tail(all_wordscores_manifesto_datasets[["wordscores_manifesto_welfare_ngram_4"]], nr_of_rows), row.names = FALSE)
```
More results:
[Unigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_1_tail.csv) |
[Bigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_2_tail.csv) |
[Trigrams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_3_tail.csv) |
[4-grams](https://github.com/fabianaiolfi/eu-policy-feedback/blob/main/lss/wordscores_manifesto_seed_words/wordscores_manifesto_welfare_ngram_4_tail.csv)

##### Wordfish

```{r echo=FALSE, message=FALSE, warning=FALSE}
full_feature_scores_df_5k_unigrams <- readRDS(file = here("lss", "wordfish_output", "full_feature_scores_df_5k_unigrams.rds"))
full_feature_scores_df_5k_bigrams <- readRDS(file = here("lss", "wordfish_output", "full_feature_scores_df_5k_bigrams.rds"))
full_feature_scores_df_10k_bigrams <- readRDS(file = here("lss", "wordfish_output", "full_feature_scores_df_10k_bigrams.rds"))
```

Wordfish is an unsupervised method, meaning that it estimates the positions of documents solely based on the observed word frequencies. Due to computational restraints, I could only process a random sample of 5k and 10k legislations while running the Wordfish model. I believe that including more or even all 70k legislations would not render much different results or would not justify the longer compute time.

The tables below display features (i.e., tokens) and their respective beta (i.e., the estimated effect of the token on the latent dimension). A positive beta value indicates that the word is more associated with the positive side of the dimension, while a negative beta value indicates association with the negative side. As the tables display below, the results are difficult to interpret. Tokens on both sides of the latent dimension (i.e., highest and lowest beta values) cannot be assigned to a political dimension.

**Wordfish Scores: Random Subsample of 5000 Legislations (Unigrams, highest and lowest beta values)**
```{r echo=FALSE, message=FALSE, warning=FALSE}
full_feature_scores_df_5k_unigrams %>% select(-psi) %>% arrange(-beta) %>% head(10)
full_feature_scores_df_5k_unigrams %>% select(-psi) %>% arrange(beta) %>% head(10)
```

**Wordfish Scores: Random Subsample of 5000 Legislations (Bigrams, highest and lowest beta values)**
```{r echo=FALSE, message=FALSE, warning=FALSE}
full_feature_scores_df_5k_bigrams %>% select(-psi) %>% arrange(-beta) %>% head(10)
full_feature_scores_df_5k_bigrams %>% select(-psi) %>% arrange(beta) %>% head(10)
```

**Wordfish Scores: Random Subsample of 10,000 Legislations (Bigrams, highest and lowest beta values)**
```{r echo=FALSE, message=FALSE, warning=FALSE}
full_feature_scores_df_10k_bigrams %>% select(-psi) %>% arrange(-beta) %>% head(10)
full_feature_scores_df_10k_bigrams %>% select(-psi) %>% arrange(beta) %>% head(10)
```

##### Evaluation
Both methods do not return satisfying results. Some terms returned by Wordscores faintly resemble the manual seed words. On the other hand, almost all terms returned by Wordfish cannot be assigned to a clear political side or topic. The Wordscore and Wordfish seed words will not be applied in the LSS method for the time being.

#### LSS Evaluation

How well can LSS measure the left-right polarity of EU policies? To answer this question, I analyse the keywords that are attached to each document. The EU gives each policy a set of keywords that describe the policy's content. If LSS works correctly, then the keywords should be associated with economic left/right terms. There are two sets of keywords, as described in the [dataset’s codebook](https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/0EGYWY/RVEJU9&version=2.0):

1. EUROVOC: A group of EuroVoc keywords associated with the act. See [here](https://op.europa.eu/en/web/eu-vocabularies) for details
2. Subject Matter: Group of keywords representing the subject matter of the act. Similar to EUROVOC, only less detailed, more abstract.

LSS calculates a polarity score for each document. Values range between -1.5 and +2. A negative score is associated with economic right terms, a positive score with economic left terms. I create three bins of equal width, containing an unequal number of observations and label them "left", "centre" and "right".

**Number of documents per bin**
Economy
```
centre   left  right 
 68019   6277    438 
```

Social
```
centre   left  right 
 26580  47133   1021 
```

**Most frequent keywords in economic "left" bin**
```
  EUROVOC_Keyword     Occurences
1 PDO                        502
2 product description        467
3 blockade                   452
4 ban on sales               433
5 economic sanctions         425

  Subject_matter_Keyword Occurences
1 marketing                    1515
2 agricultural policy          1029
3 health                       1021
4 agricultural activity         804
5 consumption                   790
```

**Most frequent keywords in social "left" bin**
```
  EUROVOC_Keyword          Occurences
1 Community aid to exports       5934
2 entry price                    5263
3 aubergine                      5243
4 citron                         5190
5 apple                          4686

    Subject_matter_Keyword Occurences
1 plant product               13369
2 trade policy                10386
3 prices                       7992
4 trade                        7936
5 tariff policy                7351
```

**Most frequent keywords in economic "centre" bin**
```
  EUROVOC_Keyword            Occurences
1 Community aid to exports         7570
2 automatic public tendering       5558
3 entry price                      5514
4 aubergine                        5463
5 citron                           5371

  Subject_matter_Keyword Occurences
1 plant product               17042
2 trade policy                14421
3 trade                       10926
4 tariff policy               10286
5 prices                       9357
```

**Most frequent keywords in social "centre" bin**
```
  EUROVOC_Keyword            Occurences
1 Community aid to exports         1649
2 automatic public tendering       1472
3 import                           1453
4 sea fish                         1434
5 catch plan                       1313

  Subject_matter_Keyword Occurences
1 trade policy                 4444
2 plant product                3961
3 Europe                       3905
4 trade                        3204
5 tariff policy                3088
```

**Most frequent keywords in economic "right" bin**
```
  EUROVOC_Keyword            Occurences
1 beef                               80
2 automatic public tendering         59
3 floor price                        48
4 EC country                         44
5 CCT duties                         41

  Subject_matter_Keyword Occurences
1 trade policy                  145
2 animal product                 84
3 prices                         80
4 Europe                         75
5 trade                          67
```

**Most frequent keywords in social "right" bin**
```
  EUROVOC_Keyword         Occurences
1 agri-foodstuffs product         99
2 food product safety             97
3 fungicide                       85
4 blockade                        71
5 agricultural product            69

  Subject_matter_Keyword Occurences
1 marketing                     165
2 tariff policy                 158
3 agricultural activity         146
4 trade policy                  125
5 foodstuff                     123
```

As a comparison, here are the most frequent keywords overall:
```
  EUROVOC_Keyword            Occurences
1 Community aid to exports         7590
2 automatic public tendering       5633
3 entry price                      5518
4 aubergine                        5481
5 citron                           5387

  Subject_matter_Keyword Occurences
1 plant product               17447
2 trade policy                14955
3 trade                       11202
4 tariff policy               10597
5 prices                       9460
```

**Economy vs Social Scores**

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Create plot dataframe
plot_df <- glove_polarity_scores_econ %>% 
  rename(avg_glove_polarity_scores_econ = avg_glove_polarity_scores) %>% 
  left_join(glove_polarity_scores_social, by = "CELEX") %>% 
  rename(avg_glove_polarity_scores_social = avg_glove_polarity_scores) %>% 
  left_join(select(all_dir_reg, CELEX, Act_type)) %>% 
  mutate(Act_type = as.factor(Act_type))

ggplot(plot_df, aes(x = avg_glove_polarity_scores_econ, y = avg_glove_polarity_scores_social, color = Act_type)) +
  geom_jitter(size = 1, alpha = 0.2, width = 0.1, height = 0.1) + 
  labs(x = "Economy Score", y = "Social Score") +
  theme_minimal()

unique(ceps_eurlex_Subject_matter_cluster_names$subject_matter_cluster_name)
unique(ceps_eurlex_dir_reg_keywords$Subject_matter)
```

#### Results
A first analysis of the results shows that the keywords partially align with typical economic left/right terms. Keywords like “equal opportunity”, “State pension”, “employment”, “labour market” and “social protection” fit well with an economic left ideology, while “trade policy”, “tariff policy” and “international trade” can be more strongly associated with an economic right ideology.

However, there are keywords that appear to have no ideological connotation but still appear in the “most frequent” list, e.g., “exchange of information”, “beef” or “Europe”. This indicates that the polarity score calculated by LSS has its flaws.

Eyeballing the results, I feel that the Subject Matter keywords are more suitable for the evaluation than the EUROVOC keywords. This may be due to the Subject Matter keywords being more general than EUROVOC and thus capturing broader meanings. The results show that the Subject Matter keywords align better with my expectations, likely because their general nature allows them to capture a wider range of topics and themes within the dataset, while the EUROVOC keywords are too specific to do this.
