### Latent Semantic Scaling (LSS)

LSS is a method for measuring the semantic similarity between documents and a set of seed words. In our case, each directive or regulation is a document and the seed words convey "typical" left-right terms. I apply these seed words:

```{r echo=FALSE, message=FALSE, warning=FALSE}
dict <- dictionary(file = here("lss", "left_right_v3.yml"))
seed <- as.seedwords(dict$ideology, concatenator = " ")
```

**Economic left seed words**
```{r echo=FALSE, message=FALSE, warning=FALSE}
left_terms <- seed[seed == 1]
left_terms <- names(left_terms)
left_terms
```
**Economic right seed words**
```{r echo=FALSE, message=FALSE, warning=FALSE}
right_terms <- seed[seed == -1]
right_terms <- names(right_terms)
right_terms
```

#### Evaluation

How well can LSS measure the left-right polarity of EU policies? To answer this question, I analyse the keywords that are attached to each document. The EU gives each policy a set of keywords that describe the policy's content. If LSS works correctly, then the keywords should be associate with economic left/right terms. There are two sets of keywords, as described in the [CEPS EurLex codebook](https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/0EGYWY/RVEJU9&version=2.0):

1. EUROVOC: A group of EuroVoc keywords associated with the act. See [here](https://op.europa.eu/en/web/eu-vocabularies) for details
2. Subject matter: Group of keywords representing the subject matter of the act. Similar to EUROVOC, only less detailed, more abstract.

LSS calculates a polarity score for each document. Values range between -1.5 and +2. A negative score is associated with economic right terms, a positive score with economic left terms. I create three bins of equal width, containing an unequal number of observations and label them "left", "centre" and "right".

```
centre   left  right 
  9760     98    142 
```

**Most frequent keywords in "left" bin**
```
   EUROVOC_Keyword            Occurences
 1 Community statistics               13
 2 exchange of information             9
 3 compiling data                      7
 4 equal opportunity                   7
 5 national insurance                  7
 6 statistical harmonisation           7
 7 disclosure of information           6
 8 EC auxiliary staff                  5
 9 State pension                       5
10 administrative cooperation          5

   Subject_matter_Keyword                     Occurences
 1 employment                                         20
 2 information technology and data processing         17
 3 labour market                                      16
 4 economic analysis                                  14
 5 executive power and public service                 14
 6 information and information processing             14
 7 EU institutions and European civil service         12
 8 rights and freedoms                                12
 9 international law                                  11
10 social protection                                  11
```

**Most frequent keywords in "centre" bin**
```
  EUROVOC_Keyword            Occurences
 1 Community aid to exports         1106
 2 aubergine                         786
 3 entry price                       783
 4 citron                            767
 5 automatic public tendering        749
 6 import                            718
 7 apple                             696
 8 Community import                  506
 9 import authorisation              491
10 CCT duties                        473

   Subject_matter_Keyword Occurences
 1 plant product                2482
 2 trade policy                 2149
 3 trade                        1608
 4 tariff policy                1497
 5 prices                       1325
 6 agricultural policy          1208
 7 Europe                       1203
 8 foodstuff                    1074
 9 marketing                     874
10 cooperation policy            870
```

**Most frequent keywords in "right" bin**
```
   EUROVOC_Keyword            Occurences
 1 beef                               34
 2 automatic public tendering         23
 3 EC country                         16
 4 intervention agency                14
 5 offering for sale                  14
 6 floor price                        10
 7 import                             10
 8 selling price                      10
 9 CCT duties                          9
10 Community import                    8

   Subject_matter_Keyword Occurences
 1 trade policy                   41
 2 animal product                 36
 3 trade                          32
 4 Europe                         25
 5 marketing                      23
 6 prices                         20
 7 tariff policy                  17
 8 economic geography             16
 9 European construction          14
10 international trade            13
```

As a comparison, here are the most frequent keywords overall:
```
   EUROVOC_Keyword            Occurences
 1 Community aid to exports         1106
 2 aubergine                         786
 3 entry price                       785
 4 automatic public tendering        772
 5 citron                            767
 6 import                            729
 7 apple                             696
 8 Community import                  514
 9 import authorisation              499
10 CCT duties                        482

   Subject_matter_Keyword Occurences
   <chr>                       <int>
 1 plant product                2494
 2 trade policy                 2192
 3 trade                        1641
 4 tariff policy                1515
 5 prices                       1346
 6 Europe                       1233
 7 agricultural policy          1221
 8 foodstuff                    1082
 9 marketing                     904
10 cooperation policy            883
```

In a next step, I measure the correlation between the polarity scores and keywords. In other words: How much do the keywords correlate with the polarity scores? A positive correlation should be associated with economic left terms, while a negative correlation should be associated with economic right terms.

**Top positive correlations**
```
   correlation_with_scores                  EUROVOC
1                0.1593743                 blockade
2                0.1477281       economic sanctions
3                0.1344094             ban on sales
4                0.1328099  exchange of information
5                0.1272232                       NA
6                0.1266202                      PDO
7                0.1219182      product description
8                0.1148520 elimination of terrorism
9                0.1090292     Community statistics
10               0.1031237  agri-foodstuffs product

   correlation_with_scores                             Subject_matter
1                0.1982763                                     health
2                0.1746146                                 employment
3                0.1695153                                  marketing
4                0.1656535 EU institutions and European civil service
5                0.1523293     information and information processing
6                0.1510933                      international affairs
7                0.1510488 information technology and data processing
8                0.1507761                              labour market
9                0.1447519                 politics and public safety
10               0.1445159           means of agricultural production
```

**Top negative correlations**
```
     correlation_with_scores                    EUROVOC
2499              -0.1387161                      grape
2500              -0.1485295                        CMO
2501              -0.1519911                    apricot
2502              -0.1526409           Community import
2503              -0.1745075 automatic public tendering
2504              -0.1756601       agri-monetary policy
2505              -0.2747642                      apple
2506              -0.2758296                  aubergine
2507              -0.2770651                     citron
2508              -0.2925299                entry price

    correlation_with_scores                         Subject_matter
117             -0.05063899 iron, steel and other metal industries
118             -0.05172661                            soft energy
119             -0.05609725                    beverages and sugar
120             -0.05759779                                America
121             -0.05950036                            competition
122             -0.09135739                    agricultural policy
123             -0.18789545                           trade policy
124             -0.20253832                                  trade
125             -0.31335321                          plant product
126             -0.33752753                                 prices
```

