---
title: "Evaluation of Summaries compared to Nanou 2017 (Ground Truth)"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(corrplot)
library(reshape2)
library(Metrics)
library(kableExtra)
library(car)
```

```{r, include=FALSE}
broad_policy_mpolicy_avg_df <- readRDS(here("data", "evaluation", "broad_policy_mpolicy_avg_df_summaries.rds"))
broad_policy_mpolicy_avg_df <- broad_policy_mpolicy_avg_df %>% 
  drop_na() %>% 
  mutate(nanou_2017_mpolicy_lrscale3 = as.numeric(nanou_2017_mpolicy_lrscale3)) %>% 
  rename("LSS Economy" = avg_lss_econ_z_score) %>% 
  rename("LSS Social" = avg_lss_social_z_score) %>% 
  rename("RoBERT Left Right" = RoBERT_left_right_z_score) %>% 
  rename("Bakker Hobolt Economy" = bakker_hobolt_econ_z_score) %>% 
  rename("Bakker Hobolt Social" = bakker_hobolt_social_z_score) %>% 
  rename("CMP Left Right" = cmp_left_right_z_score) %>% 
  rename("ChatGPT 0-Shot" = chatgpt_summary_0_shot_z_score) %>% 
  rename("ChatGPT Ranking" = chatgpt_ranking_z_score) %>% 
  rename("Llama 0-Shot" = llama_summary_0_shot_z_score) %>% 
  rename("Llama Ranking" = llama_ranking_z_score) %>% 
  rename("Llama Ranking (3 reps)" = llama_ranking_z_score_3_reps) %>% 
  rename("Deepseek Economy 0-Shot" = deepseek_econ_0_shot_z_score) %>% 
  rename("Deepseek Social 0-Shot" = deepseek_social_0_shot_z_score) %>% 
  rename("Deepseek Ranking" = deepseek_ranking_z_score) %>% 
  rename("Nanou 2017 (Ground Truth)" = nanou_2017_mpolicy_lrscale3)

# Define the ground truth column
ground_truth <- broad_policy_mpolicy_avg_df$`Nanou 2017 (Ground Truth)`

# Select all columns to compare (excluding the ground truth column)
columns_to_compare <- broad_policy_mpolicy_avg_df %>% 
  select(-`Nanou 2017 (Ground Truth)`, -broad_policy_area_mpolicy_moodley, -period)
```

## Pearson Correlation

```{r echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}

pearson_correlation <- broad_policy_mpolicy_avg_df %>% 
  select(-broad_policy_area_mpolicy_moodley, -period)

pearson_correlation <- cor(pearson_correlation, use = "pairwise.complete.obs")
pearson_correlation_melt <- melt(pearson_correlation) # Convert the correlation matrix into long format for ggplot2

ggplot(pearson_correlation_melt, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2)), size = 3) +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab", 
                       name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1)) +
  coord_fixed() +
  xlab("") + ylab("") +
  theme(legend.position="none")
```

## Spearman's Rank Correlation

```{r echo=FALSE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE}

spearman_correlation <- broad_policy_mpolicy_avg_df %>% 
  select(-broad_policy_area_mpolicy_moodley, -period)

spearman_correlation <- cor(spearman_correlation, method = "spearman")
spearman_correlation_melt <- melt(spearman_correlation) # Convert the correlation matrix into long format for ggplot2

ggplot(spearman_correlation_melt, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2)), size = 3) +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab", 
                       name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1)) +
  coord_fixed() +
  xlab("") + ylab("") +
  theme(legend.position="none")
```


## Mean Absolute Error and Root Mean Square Error

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Calculate MAE for each column
mae_results <- sapply(columns_to_compare, function(column) {
  mean(abs(column - ground_truth), na.rm = TRUE) # Handle NA values if present
})

mae_results_df <- data.frame(
  Column = names(mae_results),
  MAE = round(mae_results, 2)
)

# Calculate RMSE for each column
rmse_results <- sapply(columns_to_compare, function(column) {
  sqrt(mean((column - ground_truth)^2, na.rm = TRUE)) # Handle NA values if present
})

rmse_results_df <- data.frame(
  Column = names(rmse_results),
  RMSE = round(rmse_results, 2)
)

errors_table <- mae_results_df %>% 
  left_join(rmse_results_df, by = "Column") %>% 
  arrange(MAE) %>% 
  rename("Mean Absolute Error" = MAE) %>% 
  rename("Root Mean Square Error" = RMSE) %>% 
  rename(" " = Column)
  
errors_table %>%
  kbl() %>%
  kable_styling()
```

## Variance

### Distribution of Z-Scores (Histograms)

```{r echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}

variance_hist <- broad_policy_mpolicy_avg_df %>%
  select(-broad_policy_area_mpolicy_moodley, -period) %>% 
  pivot_longer(cols = everything(),
               names_to = "z_score_measurement", 
               values_to = "z_score_value")

ggplot(variance_hist, aes(x = z_score_value)) +
  geom_histogram() +
  facet_wrap(~ z_score_measurement) +
  xlab("Z-Score") + ylab("Count") +
  theme_minimal()
```

### Distribution of Z-Scores (Box Plots)

```{r echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}

variance_data <- broad_policy_mpolicy_avg_df %>%
  select(-broad_policy_area_mpolicy_moodley, -period) %>% 
  pivot_longer(cols = everything(),
               names_to = "measurement", 
               values_to = "value") %>% 
  group_by(measurement)

ggplot(variance_data) +
  geom_boxplot(aes(x = measurement, y = value)) +
  ylab("Z-Score") + xlab("") +
  coord_flip() +
  theme_minimal()
```

### Levene’s Test for Equality of Variances

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Prepare a dataframe to hold the results
levene_results <- lapply(names(columns_to_compare), function(col_name) {
  # Combine ground truth and the column into a dataframe
  temp_data <- data.frame(
    value = c(ground_truth, columns_to_compare[[col_name]]),
    measurement = rep(c("Ground Truth", col_name), each = length(ground_truth))
  )
  
  # Perform Levene's Test
  test_result <- leveneTest(value ~ measurement, data = temp_data)
  
  # Extract the relevant statistics
  data.frame(
    Column = col_name,
    F_Value = test_result$`F value`[1],
    P_Value = round(test_result$`Pr(>F)`[1], 2)
  )
})

# Combine results into a single dataframe
levene_results_df <- do.call(rbind, levene_results)

levene_results_table <- levene_results_df %>% 
  select(-F_Value) %>% 
  arrange(desc(P_Value)) %>% 
  rename(" " = Column) %>% 
  rename("p-value" = P_Value)

levene_results_table %>%
  kbl() %>%
  kable_styling()
```

> If the p-value from the test is less than our chosen significance level, we can reject the null hypothesis and conclude that we have enough evidence to state that the variance among the groups is not equal.

## Adjusted MAE And RMSE With Variance Penalties
> Calculate MAE and RMSE while penalizing scores for their lack of variance, we can adjust the metrics by multiplying them by the inverse of the variance ratio. The variance ratio can be defined as the ratio of the variance of the ground truth to the variance of the other column.
> Measurements with a high spread (variance) are less penalized and are effectively "rewarded."
> Measurements with a low spread (variance) are penalized more heavily.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Function to calculate penalized MAE and RMSE
calculate_penalized_metrics <- function(column, ground_truth) {
  # Calculate variance ratio
  variance_ratio <- var(column, na.rm = TRUE) / var(ground_truth, na.rm = TRUE)

  # Avoid division by zero or very small variance
  if (is.na(variance_ratio) || variance_ratio == Inf) variance_ratio <- 1
  
  # Calculate MAE
  mae <- mean(abs(column - ground_truth), na.rm = TRUE)
  
  # Calculate RMSE
  rmse <- sqrt(mean((column - ground_truth)^2, na.rm = TRUE))
  
  # Penalize by multiplying by the inverse of the variance ratio
  penalized_mae <- round(mae / variance_ratio, 2)
  penalized_rmse <- round(rmse / variance_ratio, 2)
  
  return(c(Penalized_MAE = penalized_mae, Penalized_RMSE = penalized_rmse))
}

# Apply the function to all columns and store the results
penalized_results <- t(sapply(columns_to_compare, calculate_penalized_metrics, ground_truth = ground_truth))

penalized_results_df <- as.data.frame(penalized_results)
penalized_results_df <- penalized_results_df %>% 
  arrange(Penalized_MAE) %>% 
  rename("Penalised MAE" = Penalized_MAE) %>% 
  rename("Penalised RMSE" = Penalized_RMSE)

penalized_results_df %>%
  kbl() %>%
  kable_styling()
```


## Correlation Scatter Plots

```{r echo=FALSE, fig.height=9, fig.width=9, message=FALSE, warning=FALSE}

scatter_plot_data <- broad_policy_mpolicy_avg_df %>%
  select(-broad_policy_area_mpolicy_moodley, -period) %>% 
  pivot_longer(cols = -`Nanou 2017 (Ground Truth)`,
               names_to = "measurement", 
               values_to = "value")

ggplot(scatter_plot_data, aes(x = value, y = `Nanou 2017 (Ground Truth)`)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ x, se = F) +
  geom_abline(intercept = 0, slope = 1, color = "gray") +
  theme_minimal() +
  facet_wrap(~ measurement) +
  xlim(-2, 2) +
  xlab("")
```

