### Data Collection

The directives and regulations used in this research come from two sources. The first is the [CEPS EurLex dataset](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/0EGYWY), which contains around 70k directives and regulations from 1989 to 2019. The second source is the [EUR-Lex website](https://eur-lex.europa.eu/), an official EU website providing access to EU law. EUR-Lex can be scraped using the [`eurlex`](https://michalovadek.github.io/eurlex/) R package, which has been done to retrieve post-2019 legislation up to August 2024 (the time of writing of this report).

EUR-Lex also provides a summary for some directives and regulations (see [this example](https://eur-lex.europa.eu/legal-content/EN/LSU/?uri=CELEX:32019L0904&qid=1719922563047)). Summaries are provided on a case-by-case basis, as described [here](https://eur-lex.europa.eu/browse/summaries.html).

```{r message=FALSE, warning=FALSE, include=FALSE}
all_dir_reg <- readRDS(here("data", "data_collection", "all_dir_reg.rds"))
all_dir_reg_summaries <- readRDS(here("data", "data_collection", "all_dir_reg_summaries.rds"))
all_dir_reg <- all_dir_reg %>% left_join(all_dir_reg_summaries, by = "CELEX")
```

#### Overview Directives and Regulations

**Count of Directives and Regulations**
```{r echo=FALSE, message=FALSE, warning=FALSE}
table(all_dir_reg$Act_type)
```

**Oldest Legislation**
```{r echo=FALSE, message=FALSE, warning=FALSE}
min(all_dir_reg$Date_document)
```

**Newest Legislation**
```{r echo=FALSE, message=FALSE, warning=FALSE}
max(all_dir_reg$Date_document)
```

**Directives and Regulations by Year**
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Extract the year from the Date_document column
all_dir_reg <- all_dir_reg %>% mutate(Year = format(Date_document, "%Y"))

# Count the number of documents per Act_type per year
document_counts <- all_dir_reg %>%
  group_by(Year, Act_type) %>%
  summarise(Count = n()) %>%
  ungroup()

# Create the bar chart using ggplot2
ggplot(document_counts, aes(x = Year, y = Count, fill = forcats::fct_rev(Act_type))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "",
       x = "",
       y = "",
       fill = NULL) +  # Remove the legend's title
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(), # Remove vertical grid lines
        panel.grid.minor.x = element_blank()) + # Remove minor vertical grid lines
  scale_x_discrete(breaks = scales::pretty_breaks(n = 5)) + # Display every 5 years on the x-axis
  scale_fill_brewer(palette = "Set2") # Change the color scheme
```

#### Overview Summaries

**Number of Summaries**
```{r echo=FALSE, message=FALSE, warning=FALSE}
overview_summaries <- all_dir_reg %>% drop_na(eurlex_summary_clean)
nrow(overview_summaries)
```

**Summary Count of Regulations and Directives**
```{r echo=FALSE, message=FALSE, warning=FALSE}
table(overview_summaries$Act_type)
```

**Oldest Summary**
```{r echo=FALSE, message=FALSE, warning=FALSE}
min(overview_summaries$Date_document)
```

**Newest Summary**
```{r echo=FALSE, message=FALSE, warning=FALSE}
max(overview_summaries$Date_document)
```

**Summaries of Directives and Regulations by Year**
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Extract the year from the Date_document column
overview_summaries <- overview_summaries %>% mutate(Year = format(Date_document, "%Y"))

# Count the number of documents per Act_type per year
document_counts <- overview_summaries %>%
  group_by(Year, Act_type) %>%
  summarise(Count = n()) %>%
  ungroup()

# Create the bar chart using ggplot2
ggplot(document_counts, aes(x = Year, y = Count, fill = forcats::fct_rev(Act_type))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "",
       x = "",
       y = "",
       fill = NULL) +  # Remove the legend's title
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(), # Remove vertical grid lines
        panel.grid.minor.x = element_blank()) + # Remove minor vertical grid lines
  scale_x_discrete(breaks = scales::pretty_breaks(n = 5)) + # Display every 5 years on the x-axis
  scale_fill_brewer(palette = "Set2") # Change the color scheme
```
