### Recreating Hix Høyland (2024)

```{r message=FALSE, warning=FALSE, include=FALSE}
hix_hoyland_data <- readRDS(here("existing_measurements", "hix_hoyland_2024", "hix_hoyland_data.rds"))
hix_hoyland_data_summaries <- readRDS(here("existing_measurements", "hix_hoyland_2024", "hix_hoyland_data_summaries.rds"))
```

**Distribution of Ideological Values: All Directives and Regulations (N = 74,734)**  
*Please note the log-scaled y-axis*  
*Negative values: More left*  
*Positive values: More right*  
*Dotted red line highlights ideological middle (value of 0)*  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Reshape the data to long format
long_df <- hix_hoyland_data %>%
  select(-CELEX) %>% 
  pivot_longer(cols = everything(), 
               names_to = "variable", 
               values_to = "value")

ggplot(long_df, aes(x = value, fill = variable)) +
  geom_histogram(binwidth = 0.2, show.legend = FALSE) +
  scale_y_log10(labels = label_comma()) +
  xlim(-5, 5) +
  facet_wrap(~ variable) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "red",
             size = 0.25) +
  theme_minimal() +
  labs(x = "Value", y = "Count") +
  scale_fill_brewer(palette = "Set2")
```

**Distribution of Ideological Values: Summaries (N = 1637)**  
*Please note the log-scaled y-axis*  
*Negative values: More left*  
*Positive values: More right*  
*Dotted red line highlights ideological middle (value of 0)*  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Reshape the data to long format
long_df <- hix_hoyland_data_summaries %>%
  select(-CELEX) %>% 
  pivot_longer(cols = everything(), 
               names_to = "variable", 
               values_to = "value")

ggplot(long_df, aes(x = value, fill = variable)) +
  geom_histogram(binwidth = 0.2, show.legend = FALSE) +
  scale_y_log10(labels = label_comma()) +
  xlim(-5, 5) +
  facet_wrap(~ variable) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "red",
             size = 0.25) +
  theme_minimal() +
  labs(x = "Value", y = "Count") +
  scale_fill_brewer(palette = "Set2")
```
