### Recreating Hix Høyland (2024)

```{r message=FALSE, warning=FALSE, include=FALSE}
hix_hoyland_data <- readRDS(here("existing_measurements", "hix_hoyland_2024", "hix_hoyland_data.rds"))
hix_hoyland_data_summaries <- readRDS(here("existing_measurements", "hix_hoyland_2024", "hix_hoyland_data_summaries.rds"))
```

#### Distribution of Ideological Values
**All Directives and Regulations (N = 74,734)**  
*Please note the log-scaled y-axis*  
*Negative values: More left*  
*Positive values: More right*  
*Dotted red line highlights ideological middle (value of 0)*  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Reshape the data to long format
long_df <- hix_hoyland_data %>%
  select(-CELEX) %>% 
  pivot_longer(cols = everything(), 
               names_to = "variable", 
               values_to = "value")

ggplot(long_df, aes(x = value, fill = variable)) +
  geom_histogram(binwidth = 0.2, show.legend = FALSE) +
  scale_y_log10(labels = label_comma()) +
  xlim(-5, 5) +
  facet_wrap(~ variable) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "red",
             size = 0.25) +
  theme_minimal() +
  labs(x = "Value", y = "Count") +
  scale_fill_brewer(palette = "Set2")
```

**All Summaries (N = 1637)**  
*Please note the log-scaled y-axis*  
*Negative values: More left*  
*Positive values: More right*  
*Dotted red line highlights ideological middle (value of 0)*  
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Reshape the data to long format
long_df <- hix_hoyland_data_summaries %>%
  select(-CELEX) %>% 
  pivot_longer(cols = everything(), 
               names_to = "variable", 
               values_to = "value")

ggplot(long_df, aes(x = value, fill = variable)) +
  geom_histogram(binwidth = 0.2, show.legend = FALSE) +
  scale_y_log10(labels = label_comma()) +
  xlim(-5, 5) +
  facet_wrap(~ variable) +
  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "red",
             size = 0.25) +
  theme_minimal() +
  labs(x = "Value", y = "Count") +
  scale_fill_brewer(palette = "Set2")
```

#### Comparing Preamble with Summaries

```{r message=FALSE, warning=FALSE, include=FALSE}
# Merge preamble and summary dataframes
comparison <- hix_hoyland_data_summaries %>% 
  rename(RoBERT_left_right_summary = RoBERT_left_right,
         bakker_hobolt_econ_summary = bakker_hobolt_econ,
         bakker_hobolt_social_summary = bakker_hobolt_social,
         cmp_left_right_summary = cmp_left_right) %>% 
  left_join(hix_hoyland_data, by = "CELEX") %>% 
  rename(RoBERT_left_right_preamble = RoBERT_left_right,
         bakker_hobolt_econ_preamble = bakker_hobolt_econ,
         bakker_hobolt_social_preamble = bakker_hobolt_social,
         cmp_left_right_preamble = cmp_left_right)
```

**Scatter Plot with Line of Equality**  
*Red dashed line of equality shows where the values from the preamble and the summary would be equal. Points below the line indicate that preamble value is greater than the summary value (i.e., more right), and points above indicate the opposite. Plot applies jitter in order to counteract overlapping points (e.g., at `0,0`).*
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Define the pairs of preamble and summary columns
prefixes <- c("RoBERT_left_right", "bakker_hobolt_econ", "bakker_hobolt_social", "cmp_left_right")

# Function to generate the scatter plot for each pair
generate_plot <- function(prefix) {
  ggplot(comparison, aes_string(x = paste0(prefix, "_preamble"), y = paste0(prefix, "_summary"))) +
    geom_jitter(size = 1, alpha = 0.3, width = 0.1, height = 0.1) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
    labs(x = "Preamble", y = "Summary", subtitle = prefix) +
    theme_minimal()
}

# Generate the plots and display them
plots <- map(prefixes, generate_plot)
plot_grid(plotlist = plots, ncol = 2)
```

**Mean-Difference Plot (Bland-Altman Plot)**  
*Red dashed line of equality shows where the values from the preamble and the summary would be equal. Points below the line indicate that preamble value is lower than the summary value (i.e., more left), and points above indicate the opposite. Plot applies jitter in order to counteract overlapping points.*
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Function to generate the Bland-Altman plot for each pair
generate_bland_altman_plot <- function(prefix) {
  df <- comparison %>%
    mutate(mean_value = (get(paste0(prefix, "_preamble")) + get(paste0(prefix, "_summary"))) / 2,
           difference = get(paste0(prefix, "_preamble")) - get(paste0(prefix, "_summary")))
  
  ggplot(df, aes(x = mean_value, y = difference)) +
    geom_jitter(size = 1, alpha = 0.3, width = 0.1, height = 0.1) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    labs(x = "Mean of Preamble and Summary", y = "Preamble - Summary",
         subtitle = prefix) +
    theme_minimal()
}

bland_altman_plots <- map(prefixes, generate_bland_altman_plot)
plot_grid(plotlist = bland_altman_plots, ncol = 2)
```


